Data exploration, quality control and statistical analysis of ChIP-exo experiments

### 2015-11-30 rmarkdown/prelims_paper.Rnw
second draft of slides

Table \ref{tab:qcbase} contains measures that are commonly used with
ChIP-Seq data. PBC stands for PCR bottleneck amplification and is
defined as the ratio between the number of positions to which exactly
one mapping read maps divided by the number of position to which at
least one mapping reads maps, the ENCODE project proposed a series of
ranges to interpret this quantity (which can be found in
\url{https://www.encodeproject.org/data-standards/2012-quality-metrics/}),
but it doesn't apply to ChIP-exo, if it did all the samples with
$\mbox{PBC} < 0.5$ should be reject due to be showing severe
bottlenecking. The normalized strand cross-correlation (NSC) is
defined as:

@@

Figure \ref{fig:scc} shows the SCC function for both a ChIP-exo (in
red) and a SE ChIP-Seq (in green) for CTCF in HeLa cell line. The
ChIP-Seq dataset behaves as the successful case from \cite{encode_qc},
but the ChIP-exo doesn't. Additionally, since the exonuclease enzyme
digests the DNA fragments, then the shifts where the SCC may reach a
local or a global maximum are confounded. Hence, new QC measures are
necessary for ChIP-exo data.

@@

The strand imbalance assessment is based in the observation that the
enriched regions usually have a higher concentration of reads,
therefore we examined the FSR (defined as the ratio of the number of
forward stranded reads divided by the total number of reads in a given
region) as the region with lower depth are being filtered out. This
indicator is of particular importance, since several methods rely on
the ``peak-pair'' assumption. In Table \ref{tab:qcbase}, we calculated
the FSR and noticed that for all the samples, it's value is close to
0.5, which means that there are roughly the same amount of reads in
both strands. However, Figure \ref{fig:comp}B shows that this value
doesn't represent the sample locally, hence the assumption doesn't
hold well in practice.

@@

In order to assess the strand imbalance we created the following
visualization presented in Figure \ref{fig:strand}. A) shows the FSR's
behavior as lower depth regions are being filtered out, while B) shows
which percentage of the regions are composed by reads of both strands
or only one (forward or backward). As the number of reads per region's
lower bound increases, the quantiles tend to approach the median. To
evaluate this statement, for each replicate of FoxA1, we divided the
regions formed by at least \Sexpr{de} reads into the ones that overlap
with any of the sample's peaks. Then we considered Kolmogorov-Smirnov
tests to assess if the FSR's distribution was the same for the islands
that overlap with a peak and the islands that didn't. The p.value for
the third replicate's test is \Sexpr{pval[[1]]}, for the first
replicate's test is \Sexpr{pval[[2]]} and for the second test is
\Sexpr{pval[[3]]}. This shows that only the middle sample from Figure
\ref{fig:strand} is the least imbalance sample from the the three,
while the other two still show a higher imbalance at the \Sexpr{de}
level.

@@

Previously, ChIP-exo and SE ChIP-Seq have been compared at a fixed
depth level in the literature, but this comparisons didn't included PE
ChIP-Seq. Hence, we sampled a fixed amount of reads for each of the
ChIP-exo, PE ChIP-Seq and SE ChIP-Seq datasets of the $\sigma^{70}$
sample in aerobic conditions. For each sampled dataset we applied our
lower-to-higher resolution pipeline by calling peaks with MOSAiCS
\cite{mosaics} and then deconvolving the binding events by using dPeak
\cite{dpeak}. For the ChIP-exo datasets we called peaks by using
GC-content and mappability with MOSAiCS, and for the ChIP-Seq datasets
we used their respective Input samples.

@@

@@

We provide a ChIP-exo QC pipeline capable of assess the balance
between enriched samples and low complexity regions. It is shown that
the ``peak-pair'' assumption doesn't hold locally in practice and we
provide two out-of-the-box visualization capable to assess the strand
imbalance in a ChIP-exo experiment.

@@

The data showed in Figure \ref{fig:exo_example} is actually part of a
more interesting experiment from Professor Landick's lab. We have 2
biological replicates of the $\sig$, $\beta'_f$ and $\beta$
transcription factors under two conditions, one where rifampicin was
applied by 20 minutes and another where it wasn't applied. As seen in
the Figure, there is ChIP-exo data for the 3 factors and PE ChIP-Seq
for $\sig$ and $\beta'_f$ (in the Figure both replicates were pooled).

>>>>

Table \ref{tab:qcbase} contains measures that are commonly used with
ChIP-Seq data. PBC stands for PCR bottleneck amplification and is
defined as the ratio between the number of positions to which exactly
one mapping read maps divided by the number of position to which at
least one mapping reads maps, the ENCODE project proposed a series of
ranges to interpret this quantity (which can be found in
\url{https://www.encodeproject.org/data-standards/2012-quality-metrics/}),
but it does not apply to ChIP-exo, if it did all the samples with
$\mbox{PBC} < 0.5$ should be reject due to be showing severe
bottlenecking. The normalized strand cross-correlation (NSC) is
defined as:

@@

Figure \ref{fig:scc} shows the SCC function for both a ChIP-exo (in
red) and a SE ChIP-Seq (in green) for CTCF in HeLa cell line. The
ChIP-Seq dataset behaves as the successful case from \cite{encode_qc},
but the ChIP-exo does not. Additionally, since the exonuclease enzyme
digests the DNA fragments, then the shifts where the SCC may reach a
local or a global maximum are confounded. Hence, new QC measures are
necessary for ChIP-exo data.

@@

The strand imbalance assessment is based in the observation that the
enriched regions usually have a higher concentration of reads,
therefore we examined the FSR (defined as the ratio of the number of
forward stranded reads divided by the total number of reads in a given
region) as the region with lower depth are being filtered out. This
indicator is of particular importance, since several methods rely on
the ``peak-pair'' assumption. In Table \ref{tab:qcbase}, we calculated
the FSR and noticed that for all the samples, it's value is close to
0.5, which means that there are roughly the same amount of reads in
both strands. However, Figure \ref{fig:comp}B shows that this value
does not represent the sample locally, hence the assumption does not
hold well in practice.

@@

In order to assess the strand imbalance we created the following
visualization presented in Figure \ref{fig:strand}. A) shows the FSR's
behavior as lower depth regions are being filtered out, while B) shows
which percentage of the regions are composed by reads of both strands
or only one (forward or backward). As the number of reads per region's
lower bound increases, the quantiles tend to approach the median. To
evaluate this statement, for each replicate of FoxA1, we divided the
regions formed by at least \Sexpr{de} reads into the ones that overlap
with any of the sample's peaks. Then we considered Kolmogorov-Smirnov
tests to assess if the FSR's distribution was the same for the islands
that overlap with a peak and the islands that did not. The p.value for
the third replicate's test is \Sexpr{pval[[1]]}, for the first
replicate's test is \Sexpr{pval[[2]]} and for the second test is
\Sexpr{pval[[3]]}. This shows that only the middle sample from Figure
\ref{fig:strand} is the least imbalance sample from the the three,
while the other two still show a higher imbalance at the \Sexpr{de}
level.

@@

Previously, ChIP-exo and SE ChIP-Seq have been compared at a fixed
depth level in the literature, but this comparisons did not included PE
ChIP-Seq. Hence, we sampled a fixed amount of reads for each of the
ChIP-exo, PE ChIP-Seq and SE ChIP-Seq datasets of the $\sigma^{70}$
sample in aerobic conditions. For each sampled dataset we applied our
lower-to-higher resolution pipeline by calling peaks with MOSAiCS
\cite{mosaics} and then deconvolving the binding events by using dPeak
\cite{dpeak}. For the ChIP-exo datasets we called peaks by using
GC-content and mappability with MOSAiCS, and for the ChIP-Seq datasets
we used their respective Input samples.

@@

% \subsection{Comparison with other algorithms}
% \label{sec:comp_algo}

% \begin{figure}[H]
%   \centering
%   \includegraphics[width = .5\textwidth]{../figs/for_paper/algorithm_resolution.pdf}
%   \caption{Comparison of resolution of the algorithms for ChIP-exo
%     data, using regulonDB annotations as a gold standard.}
%   \label{fig:algor}
% \end{figure}

@@

We provide a ChIP-exo QC pipeline capable of assess the balance
between enriched samples and low complexity regions. It is shown that
the ``peak-pair'' assumption does not hold locally in practice and we
provide two out-of-the-box visualization capable to assess the strand
imbalance in a ChIP-exo experiment.

@@

The data showed in Figure \ref{fig:exo_example} is actually part of a
more interesting experiment from Professor Landick's lab. We have 2
biological replicates of the $\sig$, $\beta'_f$ and $\beta$
transcription factors under two conditions, one where rifampicin was
applied by 20 minutes and another where it was not applied. As seen in
the Figure, there is ChIP-exo data for the 3 factors and PE ChIP-Seq
for $\sig$ and $\beta'_f$ (in the Figure both replicates were pooled).

### 2015-11-30 rmarkdown/prelims_paper.tex
second draft of slides

The strand imbalance assessment is based in the observation that the
enriched regions usually have a higher concentration of reads,
therefore we examined the FSR (defined as the ratio of the number of
forward stranded reads divided by the total number of reads in a given
region) as the region with lower depth are being filtered out. This
indicator is of particular importance, since several methods rely on
the ``peak-pair'' assumption. In Table \ref{tab:qcbase}, we calculated
the FSR and noticed that for all the samples, it's value is close to
0.5, which means that there are roughly the same amount of reads in
both strands. However, Figure \ref{fig:comp}B shows that this value
doesn't represent the sample locally, hence the assumption doesn't
hold well in practice.

In order to assess the strand imbalance we created the following
visualization presented in Figure \ref{fig:strand}. A) shows the FSR's
behavior as lower depth regions are being filtered out, while B) shows
which percentage of the regions are composed by reads of both strands
or only one (forward or backward). As the number of reads per region's
lower bound increases, the quantiles tend to approach the median. To
evaluate this statement, for each replicate of FoxA1, we divided the
regions formed by at least 100 reads into the ones that overlap
with any of the sample's peaks. Then we considered Kolmogorov-Smirnov
tests to assess if the FSR's distribution was the same for the islands
that overlap with a peak and the islands that didn't. The p.value for
the third replicate's test is 0.1039, for the first
replicate's test is 0.0064 and for the second test is
0.0871. This shows that only the middle sample from Figure
\ref{fig:strand} is the least imbalance sample from the the three,
while the other two still show a higher imbalance at the 100
level.

>>>>

The strand imbalance assessment is based in the observation that the
enriched regions usually have a higher concentration of reads,
therefore we examined the FSR (defined as the ratio of the number of
forward stranded reads divided by the total number of reads in a given
region) as the region with lower depth are being filtered out. This
indicator is of particular importance, since several methods rely on
the ``peak-pair'' assumption. In Table \ref{tab:qcbase}, we calculated
the FSR and noticed that for all the samples, it's value is close to
0.5, which means that there are roughly the same amount of reads in
both strands. However, Figure \ref{fig:comp}B shows that this value
does not represent the sample locally, hence the assumption does not
hold well in practice.

In order to assess the strand imbalance we created the following
visualization presented in Figure \ref{fig:strand}. A) shows the FSR's
behavior as lower depth regions are being filtered out, while B) shows
which percentage of the regions are composed by reads of both strands
or only one (forward or backward). As the number of reads per region's
lower bound increases, the quantiles tend to approach the median. To
evaluate this statement, for each replicate of FoxA1, we divided the
regions formed by at least 100 reads into the ones that overlap
with any of the sample's peaks. Then we considered Kolmogorov-Smirnov
tests to assess if the FSR's distribution was the same for the islands
that overlap with a peak and the islands that did not. The p.value for
the third replicate's test is 0.1039, for the first
replicate's test is 0.0064 and for the second test is
0.0871. This shows that only the middle sample from Figure
\ref{fig:strand} is the least imbalance sample from the the three,
while the other two still show a higher imbalance at the 100
level.

### 2015-11-30 rmarkdown/slides.Rnw
second draft of slides

@@

% Personal Data

@@

  \begin{enumerate}
\only<1>{
  \item Partition the genome and generate ChIP-exo islands.
\begin{figure}[H]
\centering
\includegraphics[width = \textwidth]{../figs/for_paper/coverage_diagram2_part1.pdf}
\end{figure}
}
\only<2>{
\addtocounter{enumi}{1}
\item Calculate a vector of summary statistics for each islands.
\begin{figure}[H]
\centering
\includegraphics[width = \textwidth]{../figs/for_paper/coverage_diagram2_part2.pdf}
\end{figure}
}
\only<3>{
\addtocounter{enumi}{2}
\item Visualize all islands together.
\begin{figure}[H]
\centering
\includegraphics[width = \textwidth]{../figs/for_paper/coverage_diagram2_part3.pdf}
\end{figure}
}
  \end{enumerate}
\end{frame}

  % \begin{itemize}
  % \item $\mbox{ARC} = \frac{\text{Nr. of reads in the
  %       region}}{\text{Width of the region}}$
  % \item $\mbox{URCR} = \frac{\text{Nr. of reads mapped to only one
  %       position in the region}}{\text{Nr. of reads in the region}}$
  % \item $\mbox{local-NSC}$
  % \item $\mbox{FSR} = \frac{\text{Nr. of fwd. strand reads in region}}{\text{Nr. of reads in region}}$
  % \end{itemize}

\begin{frame}[t,plain]
  \frametitle{Library complexity and enrichment}
\only<1>{
\begin{figure}[H]
  \centering
  \includegraphics[width = \textwidth]{../figs/Carroll_mice_for_paper/FoxA1_enrichment.pdf}
\end{figure}
}

\only<2>{
{\small
\begin{figure}[H]
  \centering
  \includegraphics[width = \textwidth]{../figs/for_paper/local_SCC_example.pdf}
\end{figure}
}}
\only<2>{
\begin{align}
 y(\delta) = f(x_\delta) + \epsilon_\delta \quad 
\mbox{local-NSC} = \frac{max_{x_\delta} \hat{f}(x_\delta)}{\hat{\sigma}_f}
\nonumber
\end{align}
}

\only<3>{
\begin{figure}[H]
\centering
  \includegraphics[width = \textwidth,page =3]{../figs/Carroll_mice_for_paper/Local_SCC_indicator_by_strata.pdf}
\end{figure}
}

\only<3>{
{\small
where:
\begin{itemize}
\item high - regions with nr. of unique positions $ > 100$
\item med - regions with nr. of unique positions in $(50,100)$
\item low - regions with nr. of unique positions in $(20,50)$
\end{itemize}
}}

@@

@@

@@

\begin{frame}[t]
  \frametitle{dPeak model for SET case}

\only<1>{
  We consider a region with $n$ reads and $m$ positions, for the
  $i$-th read:
  \begin{itemize}
  \item $Z_i \sim \mbox{Multi}(\pi_0,\pi_1,\cdots,\pi_{g^*})$
  \item $D_i \sim \mbox{Ber}(p_D)$
    \begin{itemize}
    \item The read is in the forward strand ($D_i = 1$):
      \begin{itemize}
      \item The reads belongs to the background: $R_i | Z_i = 0, D_i =
        1 \sim \mbox{Unif}(1 - \beta + 1, m)$
      \item The read belong to the $g$-th binding event: $R_i | Z_i =
        g, D_i = 1 \sim \mbox{N}(\mu_g - \delta , \sigma^2)$
      \end{itemize}
    \item The read is in the backward strand ($D_i = 0$):
      \begin{itemize}
      \item The reads belongs to the background: $R_i | Z_i = 0, D_i =
        0 \sim \mbox{Unif}(1 , m + \beta - 1)$
      \item The read belong to the $g$-th binding event: $R_i | Z_i =
        g, D_i = 0 \sim \mbox{N}(\mu_g + \delta , \sigma^2)$
      \end{itemize}
    \end{itemize}
  \end{itemize}
}

\only<2>{
      \begin{figure}[H]
        \centering
        \includegraphics[width =
        .8\textwidth]{/p/keles/ChIPexo/volume3/ChIPexo/poster/dpeak.png}
      \end{figure}
}
\end{frame}

>>>>

\usepackage{wrapfig}

@@

% Personal Data
\def\Put(#1,#2)#3{\leavevmode\makebox(0,0){\put(#1,#2){#3}}}

@@

  \begin{enumerate}
\only<1>{
  \item Partition the genome and generate ChIP-exo islands.
\begin{figure}[H]
\centering
\includegraphics[width = \textwidth]{../figs/for_paper/coverage_diagram2_part1.pdf}
\end{figure}
}
\only<2>{
\addtocounter{enumi}{1}
\item Calculate a vector of summary statistics for each islands.
\begin{figure}[H]
\centering
\includegraphics[width = \textwidth]{../figs/for_paper/coverage_diagram2_part2.pdf}
\end{figure}
}
\only<3>{
\addtocounter{enumi}{2}
\item Visualize all islands together.
\begin{figure}[H]
\centering
\includegraphics[width = \textwidth]{../figs/for_paper/coverage_diagram2_part3P.pdf}
\end{figure}
}
  \end{enumerate}
\end{frame}

 % \begin{itemize}
  % \item $\mbox{local-NSC}$
  % \item $\mbox{FSR} = \frac{\text{Nr. of fwd. strand reads in region}}{\text{Nr. of reads in region}}$
  % \end{itemize}

\begin{frame}
  \frametitle{ARC vs. URCR exploration}
\only<1>{
  \begin{itemize}
  \item $\mbox{ARC} = \frac{\text{Nr. of reads in the
        region}}{\text{Width of the region}}$
  \item $\mbox{URCR} = \frac{\text{Nr. of reads mapped to only one
        position in the region}}{\text{Nr. of reads in the region}}$
  \end{itemize}
}
\only<2>{
All regions
  \begin{figure}[H]
    \centering
    \includegraphics[width = .7\textwidth,page = 1]{../figs/for_paper/ARC_vs_URCR_example_npos.pdf}
  \end{figure}
}

\only<3>{
Mapped to more than 10 positions
  \begin{figure}[H]
    \centering
    \includegraphics[width = .7\textwidth,page = 2]{../figs/for_paper/ARC_vs_URCR_example_npos.pdf}
  \end{figure}
}

\only<4>{
Mapped to more than 30 positions
  \begin{figure}[H]
    \centering
    \includegraphics[width = .7\textwidth,page = 3]{../figs/for_paper/ARC_vs_URCR_example_npos.pdf}
  \end{figure}
}
\only<5>{
Mapped to more than 50 positions
  \begin{figure}[H]
    \centering
    \includegraphics[width = .7\textwidth,page = 4]{../figs/for_paper/ARC_vs_URCR_example_npos.pdf}
  \end{figure}
}

@@

\begin{frame}
  \frametitle{ARC vs. URCR exploration}

\only<1-2>{
  \begin{figure}[H]
    \centering
    \includegraphics[width = .7\textwidth,page =1]{../figs/for_paper/enrichment_example.pdf}
  \end{figure}
}

\only<2>{
\Put(120,200){\includegraphics[width = .6\textwidth,page = 1]{../figs/for_paper/coverage_example.pdf}}
}

\only<3-4>{
  \begin{figure}[H]
    \centering
    \includegraphics[width = .7\textwidth,page =2]{../figs/for_paper/enrichment_example.pdf}
  \end{figure}
}

\only<4>{
\Put(120,200){\includegraphics[width = .6\textwidth,page = 2]{../figs/for_paper/coverage_example.pdf}}
}

\only<5-6>{
  \begin{figure}[H]
    \centering
    \includegraphics[width = .7\textwidth,page =3]{../figs/for_paper/enrichment_example.pdf}
  \end{figure}
}

\only<6>{
\Put(120,200){\includegraphics[width = .6\textwidth,page = 3]{../figs/for_paper/coverage_example.pdf}}
}

\only<7-8>{
  \begin{figure}[H]
    \centering
    \includegraphics[width = .7\textwidth,page = 4]{../figs/for_paper/enrichment_example.pdf}
  \end{figure}
}

\only<8>{
\Put(120,200){\includegraphics[width = .6\textwidth,page = 4]{../figs/for_paper/coverage_example.pdf}}
}

% \only<9-10>{
%   \begin{figure}[H]
%     \centering
%     \includegraphics[width = .7\textwidth,page = 5]{../figs/for_paper/enrichment_example.pdf}
%   \end{figure}
% }

% \only<10>{
% \Put(120,200){\includegraphics[width = .6\textwidth,page = 5]{../figs/for_paper/coverage_example.pdf}}
% }

\only<9-10>{
  \begin{figure}[H]
    \centering
    \includegraphics[width = .7\textwidth,page =6]{../figs/for_paper/enrichment_example.pdf}
  \end{figure}
}

\only<10>{
\Put(120,300){\includegraphics[width = .6\textwidth,page = 6]{../figs/for_paper/coverage_example.pdf}}
}

\only<11-12>{
  \begin{figure}[H]
    \centering
    \includegraphics[width = .7\textwidth,page =7]{../figs/for_paper/enrichment_example.pdf}
  \end{figure}
}

\only<12>{
\Put(120,300){\includegraphics[width = .6\textwidth,page = 7]{../figs/for_paper/coverage_example.pdf}}
}

\only<13-14>{
  \begin{figure}[H]
    \centering
    \includegraphics[width = .7\textwidth,page =8]{../figs/for_paper/enrichment_example.pdf}
  \end{figure}
}

\only<14>{
\Put(120,300){\includegraphics[width = .6\textwidth,page = 8]{../figs/for_paper/coverage_example.pdf}}
}

\begin{frame}
  \frametitle{ARC vs. URCR exploration by replicate}
\only<1>{
\begin{figure}[H]
  \centering
  \includegraphics[width = \textwidth,page = 1]{../figs/Carroll_mice_for_paper/FoxA1_enrichment.pdf}
\end{figure}
}

\only<2>{
\begin{figure}[H]
  \centering
  \includegraphics[width = \textwidth,page = 3]{../figs/Carroll_mice_for_paper/FoxA1_enrichment.pdf}
\end{figure}
}

\begin{frame}
  \frametitle{ARC vs. URCR and local-NSC}

\only<1>{
\begin{figure}[H]
  \centering
  \includegraphics[width = \textwidth,page = 1]{../figs/for_paper/local_SCC_separated.pdf}
\end{figure}
}

\only<2>{
\begin{figure}[H]
  \centering
  \includegraphics[width = \textwidth,page = 2]{../figs/for_paper/local_SCC_separated.pdf}
\end{figure}
}

\only<3>{
\begin{align}
 y(\delta) = f(x_\delta) + \epsilon_\delta, \quad 
\mbox{local-NSC} = \frac{max_{x_\delta} \hat{f}(x_\delta)}{\hat{\sigma}_f},
\nonumber
\end{align}
\vspace*{\fill}
}

\only<3>{
\begin{columns}

\column{.4\textwidth}
where:

\begin{itemize}
\item $x_\delta$ is the shift.
\item $y_\delta$ is the local - SCC at shift $x_\delta$
\item $\epsilon \sim N(0, \sigma^2)$ i.i.d 
\end{itemize}

\column{.6\textwidth}
{\scriptsize
  \begin{table}[H]
    \centering
    \begin{tabularx}{\textwidth}{ @{} l | r | r |r @{}}
      \toprule
      Replicate & $\hat{\sigma}$ & $\max_{x_\delta} \hat{f}(x_\delta)$ & $\mbox{local-NSC}$ \\
      \midrule
Rep. 1 & 0.0533 & 0.2215 & 4.14 \\
Rep. 2 & 0.0453 & 0.1606 & 3.54 \\
Rep. 3 & 0.0475 & 0.0832 & 1.75 \\
\bottomrule
    \end{tabularx}
  \end{table}
}

\end{columns}
}

\only<4>{
  \begin{figure}[H]
    \centering
      \includegraphics[width = \textwidth,page =4]{../figs/Carroll_mice_for_paper/Local_SCC_indicator_by_strata.pdf}
  \end{figure}

  \begin{itemize}
  \item {\color{RoyalBlue} high:} Number of unique positions $ > 100$
  \item {\color{RoyalBlue} med:} Number of unique positions in $(50,100)$
  \item {\color{RoyalBlue} low:} Number of unique positions in $(20,50)$
  \end{itemize}
}
\end{frame}

@@

{\scriptsize
\begin{itemize}
\item  
\end{itemize}
}
\end{frame}

\begin{frame}[plain]
  \frametitle{dPeak model for SET case}

\only<1>{

      \begin{figure}[H]
        \centering
        \includegraphics[width =
        \textwidth]{/p/keles/ChIPexo/volume3/ChIPexo/poster/dpeak.png}
      \end{figure}
}

\only<2>{
\begin{columns}[t]
\column{.3\textwidth}
  \begin{figure}[H]
    \centering
    \includegraphics[width =\textwidth]
{/p/keles/ChIPexo/volume3/ChIPexo/poster/dpeak.png}
  \end{figure}

\column{.7\textwidth}
  We consider a region with $n$ reads and $m$ positions, for the
  $i$-th read:
  \begin{itemize}
  \item $Z_i \sim \mbox{Multi}(\pi_0,\pi_1,\cdots,\pi_{g^*})$
  \item $D_i \sim \mbox{Ber}(p_D)$
    \begin{itemize}
    \item The read is in the forward strand ($D_i = 1$):
      \begin{itemize}
      \item The reads belongs to the background: $R_i | Z_i = 0, D_i =
        1 \sim \mbox{Unif}(1, m)$
      \item The read belong to the $g$-th binding event: $R_i | Z_i =
        g, D_i = 1 \sim \mbox{N}(\mu_g - \delta , \sigma^2)$
      \end{itemize}
    \item The read is in the backward strand ($D_i = 0$):
      \begin{itemize}
      \item The reads belongs to the background: $R_i | Z_i = 0, D_i =
        0 \sim \mbox{Unif}(1 , m )$
      \item The read belong to the $g$-th binding event: $R_i | Z_i =
        g, D_i = 0 \sim \mbox{N}(\mu_g + \delta , \sigma^2)$
      \end{itemize}
    \end{itemize}
  \end{itemize}
\end{columns}
}

@@

\begin{frame}
  \frametitle{Structure of the experiment}

  \begin{figure}[H]
    \centering

  \end{figure}

### 2015-11-30 rmarkdown/slides.tex
second draft of slides

\begin{frame}[t]
  \frametitle{dPeak model for SET case}

\only<1>{
  We consider a region with $n$ reads and $m$ positions, for the
  $i$-th read:
  \begin{itemize}
  \item $Z_i \sim \mbox{Multi}(\pi_0,\pi_1,\cdots,\pi_{g^*})$
  \item $D_i \sim \mbox{Ber}(p_D)$
    \begin{itemize}
    \item The read is in the forward strand ($D_i = 1$):
      \begin{itemize}
      \item The reads belongs to the background: $R_i | Z_i = 0, D_i =
        1 \sim \mbox{Unif}(1 - \beta + 1, m)$
      \item The read belong to the $g$-th binding event: $R_i | Z_i =
        g, D_i = 1 \sim \mbox{N}(\mu_g - \delta , \sigma^2)$
      \end{itemize}
    \item The read is in the backward strand ($D_i = 0$):
      \begin{itemize}
      \item The reads belongs to the background: $R_i | Z_i = 0, D_i =
        0 \sim \mbox{Unif}(1 , m + \beta - 1)$
      \item The read belong to the $g$-th binding event: $R_i | Z_i =
        g, D_i = 0 \sim \mbox{N}(\mu_g + \delta , \sigma^2)$
      \end{itemize}
    \end{itemize}
  \end{itemize}
}

\only<2>{
      \begin{figure}[H]
        \centering
        \includegraphics[width =
        .8\textwidth]{/p/keles/ChIPexo/volume3/ChIPexo/poster/dpeak.png}
      \end{figure}
}
\end{frame}

>>>>

\begin{frame}[plain]
  \frametitle{dPeak model for SET case}

\only<1>{

      \begin{figure}[H]
        \centering
        \includegraphics[width =
        \textwidth]{/p/keles/ChIPexo/volume3/ChIPexo/poster/dpeak.png}
      \end{figure}
}

\only<2>{
\begin{columns}[t]
\column{.3\textwidth}
  \begin{figure}[H]
    \centering
    \includegraphics[width =\textwidth]
{/p/keles/ChIPexo/volume3/ChIPexo/poster/dpeak.png}
  \end{figure}

\column{.7\textwidth}
  We consider a region with $n$ reads and $m$ positions, for the
  $i$-th read:
  \begin{itemize}
  \item $Z_i \sim \mbox{Multi}(\pi_0,\pi_1,\cdots,\pi_{g^*})$
  \item $D_i \sim \mbox{Ber}(p_D)$
    \begin{itemize}
    \item The read is in the forward strand ($D_i = 1$):
      \begin{itemize}
      \item The reads belongs to the background: $R_i | Z_i = 0, D_i =
        1 \sim \mbox{Unif}(1, m)$
      \item The read belong to the $g$-th binding event: $R_i | Z_i =
        g, D_i = 1 \sim \mbox{N}(\mu_g - \delta , \sigma^2)$
      \end{itemize}
    \item The read is in the backward strand ($D_i = 0$):
      \begin{itemize}
      \item The reads belongs to the background: $R_i | Z_i = 0, D_i =
        0 \sim \mbox{Unif}(1 , m )$
      \item The read belong to the $g$-th binding event: $R_i | Z_i =
        g, D_i = 0 \sim \mbox{N}(\mu_g + \delta , \sigma^2)$
      \end{itemize}
    \end{itemize}
  \end{itemize}
\end{columns}
}

\begin{frame}
  \frametitle{Structure of the experiment}

  \begin{figure}[H]
    \centering

  \end{figure}
